# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
``` {r load, echo = TRUE }
dat <- read.csv("Activity Monitoring data.csv", header = TRUE)
stepSum <- tapply(dat$steps, dat$date, sum, na.rm = TRUE)

```



## What is mean total number of steps taken per day?

``` {r,  echo = TRUE }
hist(stepSum)

```

``` {r , echo = TRUE }
m <- mean (stepSum)
med <- quanntile(stepSum, probs = 0.5)

```
Mean is `r m` and median is `r med`.



## What is the average daily activity pattern?

``` {r , echo = TRUE }
meanSteps <- tapply(dat$steps, dat$interval, mean, na,rm =T)
intervals <- dat$interval[1:length(m2)]
plot (intervals, meanSteps, type = "l")
maxIndex <- which.max (meanSteps)


```

The max value is for interval `r maxIndex`.



## Imputing missing values


``` {r , echo = TRUE }
mxNA <- sum(is.na(dat$steps))

newSteps <- dat$steps
newSteps[is.na(dat$steps}] <- 0
newDat <- cbind (newSteps, dat$date, dat$interval)

stepSum <- tapply(newDat$nweSteps, dat$date, sum)
hist(stepSum)

m <- mean (stepSum)
med <- quanntile(stepSum, probs = 0.5)

```

Mean is `r m` and median is `r med`.

Because the NA values are replaced by 0, asn the original stepSum was calculated using na.rm = T for mean argument(in tapply), there is no chage in the result.
Hence mean and the total daily steps values are unchanged.






## Are there differences in activity patterns between weekdays and weekends?



``` {r, echo = TRUE }
dt <- as.Date(newDat$date, %Y-%m-%d")
Days <- weekdays(dt)
lWEnd <- Days %in% c("Saturday", "Sunday")
Days[lWEnd] <- "weekend"

Days[!lWEnd] <- "weekday"
newDat <- cbind(newDat, wkDayEnd = Days)
 newDat$fact <- transform (newDat,factor(Days))
library(lattice)
xyplot(meanSteps ~ intervals | fact, data = newDat, type = "l")

```


